An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-06-07 poly-embed-journal/poly-embed-journal.tex
Thinking about trim for loss and cleaning up prop 7 to match the vibe

\begin{definition}[Trim]\label{def:trim-loss}
  Given a loss $L:\R \to \reals_+^\Y$ with a finite representative set, we define $\trimcover(L) = \{L(r) \mid r \in \R'\}$ given any minimum representative set $\R'$ for $L$.
\end{definition}

\begin{corollary}\label{prop:trim-loss-condition}
  Given an loss $L : \R \to \reals^\Y_+$ with finite minimum representative set $\R^*$, we have $\trimcover(L) = \{L(u) \mid u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\} =: \trimnonred(L)$. \jessie{rename with $\trimnonred$ etc.}
\end{corollary}
\begin{proof}[Sketch]
  Let $\U := \{u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$.
  The only time $\U$ contains redundant elements is if there is $u,u' \in \U$ so that $\Gamma_u = \Gamma_{u'}$.  In such a case, removing duplicate elements of $\U$ to form $\U^*$ means $\{L(u) \mid u \in \U\} = \{L(u) \mid u \in \U^*\}$ and $L|_{U'}\}$ is nonredundant, and therefore $\U^*$ is a minimum representative set by Proposition~\ref{prop:tfae-min-rep-nonredundant}, and therefore equal to $\trimcover(L)$.

@@

Defining $\trimnonred(\Gamma)$... say $L$ elicits $\Gamma$
\begin{itemize}
\item Define $u \equiv u'$ if $\Gamma_u = \Gamma_{u'}$
\item $\U_\equiv := \{[u] \mid u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$.
\item $\trimnonred$ for properties: exactly as before: $\trimnonred(\Gamma) = \{\Gamma_u \mid [u] \in \U_\equiv\}$. 
  (old) $:\mathcal{G}\to\mathcal{G}$, $\trimnonred(\Gamma):\simplex \toto \U_\equiv$ where $\trimnonred(\Gamma)_{[u]} := \Gamma_u$, i.e., $\trimnonred(\Gamma)(p) = \{[u] \mid u \in \Gamma(p)\}$. 
\item $\trimnonred:\L \to \L$ given by $\trimnonred(L):\U_\equiv\to\reals^\Y_+$ where $L([u]) = L(u)$.  \raf{Need to prove well-defined (but now it's true)}
\end{itemize} 
\raf{END NOTES}

@@

$1 \Rightarrow 2$:
Since $\gamma$ is a finite property, it has a finite minimum representative set $\Sc$.
If $\Gamma$ embeds $\gamma$ with map $\varphi$, then $\Gamma$ also has a finite representative set $\U := \varphi(\Sc)$ and $\{\gamma_s \mid s\in\Sc\} = \{\Gamma_u \mid u\in\U\}$.
\raf{Have to argue $\U$ is a minimum representative set for $\Gamma$.}
From Corollary~\ref{cor:finite-minrep-trim} on both $\gamma$ and $\Gamma$, we have $\trimnonred(\gamma) = \{\gamma_s \mid s\in\Sc\} = \{\Gamma_u \mid u\in\U\} = \trimnonred(\Gamma)$.

$2 \Rightarrow 3$:
Since $\trimnonred(\Gamma)$ is finite and covers the simplex, we have $\U_\equiv$ finite.
Consider any set $\U = \{u \mid [u] \in \U_\equiv\}$ to be a selection of elements of $\U_\equiv$ from each equivalence class.
We claim $\{\Gamma_u \mid u \in \U_\equiv\} = \{\Gamma_u \mid u \in \U\}$, and the result follows immediately.
Since $\U$ is generated by selecting elements of $\U_\equiv$, we have $\{\Gamma_u \mid u \in \U_\equiv\} \supseteq \{\Gamma_u \mid u \in \U\}$ by construction.
To see $\{\Gamma_u \mid u \in \U_\equiv\} \subseteq \{\Gamma_u \mid u \in \U\}$, consider any $u \in \U_\equiv$.
If $u \in \U$, the result follows immediately.
If $u \not \in \U$, then we know there is no report in $u' \in \U$ such that $\Gamma_{u} \subsetneq \Gamma_{u'}$ by virtue of $u \in \U_\equiv$, so we must have some $u' \in \U$ such that $\Gamma_u = \Gamma_{u'}$.
Therefore, $u \equiv u'$, so $\Gamma_u = \Gamma_{u'} \in \{\Gamma_{u'} \mid u' \in \U\}$.
Thus, there is a finite minimum representative set $\U$ such that $\trimnonred(\Gamma) = \{\Gamma_u \mid u \in \U\}$.

@@

$3 \Rightarrow 4$:
Since level sets of elicitable properties are closed, the set $\Theta = \{\Gamma_u \mid u \in \U\}$ yields a finite covering of the simplex.\jessiet{How much effort do we need to put into showing each level set is full-dimensional?}

$4 \Leftarrow 3$:
Since $\Theta$ is a finite set of full-dimensional level sets, and these level sets are affinely equivalent to the epigraph of negative risk $\mathrm{epi}(-\risk L)$, it must follow that $-\risk L$ is polyhedral (convexity follows as a property of $-\risk L$). 
By Proposition~\ref{prop:SL-minimum}, $L$ has polyhedral risk if and only if $L$ (and therefore $\Gamma$) has a finite minimum representative set $\U$.
From Proposition~\ref{prop:SL-minimum}, we also know there is a bijection between the facets of $\mathrm{epi}(-\risk L)$ (corresponding to the level sets $\theta \in \Theta$) and the level sets $\{\Gamma_u \mid u \in \U\}$, so the generated sets are equal.

>>>>

\begin{definition}[$\trimcover$]\label{def:trim-loss}
  Given a loss $L:\R \to \reals_+^\Y$ with a finite representative set, we define $\trimcover(L) = \{L(r) \mid r \in \R'\}$ given any minimum representative set $\R'$ for $L$.
\end{definition}

\begin{corollary}\label{prop:trim-loss-condition}
  Given an loss $L : \R \to \reals^\Y_+$ with finite minimum representative set $\R^*$, we have $\trimcover(L) = \{L(u) \mid u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$. 
\end{corollary}
\begin{proof}[Sketch]
  Let $\U := \{u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$.
  The only time $\U$ contains redundant elements is if there is $u,u' \in \U$ so that $\Gamma_u = \Gamma_{u'}$.  In such a case, removing duplicate elements of $\U$ to form $\U^*$ means $\{L(u) \mid u \in \U\} = \{L(u) \mid u \in \U^*\}$ and $L|_{U'}\}$ is nonredundant, and therefore $\U^*$ is a minimum representative set by Proposition~\ref{prop:tfae-min-rep-nonredundant}, and therefore equal to $\trimcover(L)$.

@@

Defining $\trimnonred(\Gamma)$... say $L$ elicits $\Gamma$
\begin{itemize}
\item Define $u \equiv u'$ if $\Gamma_u = \Gamma_{u'}$
\item $\U_\equiv := \{[u] \mid u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$.
\item $\trimnonred$ for properties: exactly as before: $\trimnonred(\Gamma) = \{\Gamma_u \mid [u] \in \U_\equiv\}$. 
  (old) $:\mathcal{G}\to\mathcal{G}$, $\trimnonred(\Gamma):\simplex \toto \U_\equiv$ where $\trimnonred(\Gamma)_{[u]} := \Gamma_u$, i.e., $\trimnonred(\Gamma)(p) = \{[u] \mid u \in \Gamma(p)\}$. 
\item $\trimnonred:\L \to \L$ given by $\trimnonred(L):\U_\equiv\to\reals^\Y_+$ where $L([u]) = L(u)$.  \raf{Need to prove well-defined (but now it's true)}
\end{itemize}

\jessie{taking a pass on writing this formally}
\begin{definition}[$\U_\equiv, \trimnonred$]\label{def:trim-equiv}
	Given a property $\Gamma : \simplex \toto \R$, we define the equivalence class of reports $u \equiv u'$ if and only if $\Gamma_u = \Gamma_{u'}$.
	Define the set $\U_\equiv := \{[u] \mid u \in \R$ such that $\neg \exists u' \in \R$ s.t. $u' \neq u, \Gamma_u \subsetneq \Gamma_{u'}\}$.
	We define $\trimnonred(\Gamma) = \{\Gamma_u \mid [u] \in \U_\equiv\}$.
\end{definition}
\raf{END NOTES}

@@

$1 \Rightarrow 2$:
Since $\gamma$ is a finite property, it has a finite minimum representative set $\Sc$.
If $\Gamma$ embeds $\gamma$ with map $\varphi$, then $\Gamma$ also has a finite representative set $\U := \varphi(\Sc)$ and $\{\gamma_s \mid s\in\Sc\} = \{\Gamma_u \mid u\in\U\}$.
\raf{Have to argue $\U$ is a minimum representative set for $\Gamma$.}
\jessie{If $\U$ was not minimum, there would be some $u' = \varphi(s')$ such that $\Gamma(p) \cap \U \setminus \{u'\} \neq \emptyset$ for all $p \in \simplex$. This is true iff $\gamma(p) \cap \Sc \setminus \{s'\}$ is non-empty for all $p \in \simplex$, contradicting the assumption that $\Sc$ is minimum. }
From Corollary~\ref{cor:finite-minrep-trim} on both $\gamma$ and $\Gamma$, we have $\trimnonred(\gamma) = \{\gamma_s \mid s\in\Sc\} = \{\Gamma_u \mid u\in\U\} = \trimnonred(\Gamma)$.

$2 \Rightarrow 3$:
Since $\trimnonred(\Gamma) = \{\Gamma_u \mid [u] \in \U_\equiv \}$ is finite and covers the simplex, $\U_\equiv$ is a finite representative set for $L$.
Consider any set $\U = \{u \mid [u] \in \U_\equiv\}$ to be a selection of elements of $\U_\equiv$ from each equivalence class.
We claim $\trimnonred(\Gamma) = \{\Gamma_u \mid u \in \U_\equiv\} = \{\Gamma_u \mid u \in \U\}$, and the result follows immediately.
%Since $\U$ is generated by selecting elements of $\U_\equiv$, we have $\{\Gamma_u \mid u \in \U_\equiv\} \supseteq \{\Gamma_u \mid u \in \U\}$ by construction.
By construction of $\U$, we just need to show $\{\Gamma_u \mid u \in \U_\equiv\} \subseteq \{\Gamma_u \mid u \in \U\}$; consider any $u \in \U_\equiv$.
%If $u \in \U$, the result follows immediately.
If $u \in \U_\equiv \setminus \U$, then we know there is no report in $u' \in \U$ such that $\Gamma_{u} \subsetneq \Gamma_{u'}$, so we must have some $u' \in \U$ such that $u \equiv u'$.
Therefore, $\Gamma_u = \Gamma_{u'} \in \{\Gamma_{u'} \mid u' \in \U\}$, yielding the result.
Thus, there is a finite minimum representative set $\U$ such that $\trimnonred(\Gamma) = \{\Gamma_u \mid u \in \U\}$ covers the simplex.

@@

$3 \Rightarrow 4$:
Since level sets of elicitable properties are closed, the set $\Theta = \{\Gamma_u \mid u \in \U\}$ yields a finite covering of the simplex.
Moreover, by Lemma~\ref{lem:finite-minrep-weakly-dominate}, we have each level set in $\{\Gamma_u \mid u \in \U\}$ full-dimensional.

$4 \Rightarrow 3$:
Since $\Theta$ is a finite set of full-dimensional level sets, and these level sets are affinely equivalent to the epigraph of negative risk $E_L$, it must follow that $-\risk L$ is polyhedral (convexity follows as a property of $-\risk L$). 
By Proposition~\ref{prop:SL-minimum}, $L$ has polyhedral risk if and only if $L$ (and therefore $\Gamma$) has a finite minimum representative set $\U$.
From Proposition~\ref{prop:SL-minimum}, we also know there is a bijection between the facets of $E_L$ (corresponding to the level sets $\theta \in \Theta$) and the level sets $\{\Gamma_u \mid u \in \U\}$, so the generated sets are equal.

$4 \Rightarrow 1$: \jessie{Why not use this? Clears up 4 -> 3 and 3 -> 1 and still have all the equalities}
Consider any set of reports $\U = \{u_1, \ldots, u_k\}$ such that $\Theta = \{\Gamma_{u_1}, \ldots, \Gamma_{u_k}\}$.
Since $\cup \Theta = \simplex$, we have $\U$ a finite representative set for $L$, so $L$ elicits $L|_\U$ by Corollary~\ref{cor:representative-embeds-restriction}, and therefore $\Gamma$ embeds $\gamma := \prop{L|_\U}$.
